Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-24 ms_pre_post.Rmd
Fix legend of Figure 2 to correspond with new figure. Add a clause in the Results to include new figure idea

For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D). For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1). When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie]. Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative. In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.

@@

![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry. The red line in (A) shows the mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations. Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis). In the last generation, mean allele value was below zero. Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population. The histogram in (B) shows females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively. While the average female was monandrous, several females were polyandrous.](figures/Pp_vals1.png)

>>>>

For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D). For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1). When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie]. Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive. In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.

@@

![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry. Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D. Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations. Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis). In the last generation, mean allele value was below (A) or above (C) zero. Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C). The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
